Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-20 doc/mc-paper.tex
mention clause deletions in related work

Verified checkers for unsatisfiability include \cite{Cruz:Filipe:et:al:16,Heule:et:al:17,Lammich:20,Tan:2021}.
The associated proofs add clauses while preserving satisfiability until the empty clause is derived.
In contrast, our proofs construct a new propositional formula, and we have to verify that it
is partitioned and is equivalent to the input.
This requires verifying additional proof steps and subtle invariants, as described in
Sections~\ref{sect:crat} and \ref{section:formally-verified-toolchain}.

>>>>

Verified checkers for unsatisfiability include \cite{Cruz:Filipe:et:al:16,Heule:et:al:17,Lammich:20,Tan:2021}.
The associated proofs add clauses while preserving satisfiability until the empty clause is derived.
In contrast, our proofs construct a new propositional formula, and we have to verify that it
is partitioned and is equivalent to the input.
This requires verifying additional proof steps, including clause deletion steps, and subtle invariants, as described in
Sections~\ref{sect:crat} and \ref{section:formally-verified-toolchain}.
